---
title: "hw5_ilz2105"
author: "Lulu Zhang"
date: "11/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

__Problem 1__ 

```{r}
library(tidyverse)
library(rvest)
library(readr)
library(broom)

set.seed(10)

```

For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"

  
```{r}
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()

clean_data = function(x) {
  if (is.numeric(x)){
    replace(x, is.na(x), round(mean(x, na.rm = TRUE), digits = 1))
  }
  else if(!is.numeric(x)){replace(x, is.na(x), "virginica")}
}


final_iris = map_df(iris_with_missing, ~clean_data(.x))
```


__Problem 2__

made a dataframe with all the file names from the `data` folder in the `_MACOSX`
folder

Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

```{r}
data = list.files(path = "./data")
read_data = function(x){
  
  str_c("./data/", x) %>% 
    read_csv(x) %>% 
    pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value"%>% 
  separate(files, into = c("arm", "observation"), sep = "_") %>% 
  mutate(
    weekly_obs = str_replace(observation, "\\.csv", "")
  )) 
}
read_data(data)
data_x = map(data, ~read_data(.x))


```

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
macosx_files = tibble(
  name = list.files(path = "./data/", all.files = TRUE, no.. = TRUE),
  path = str_c("./data/", name))

read_data = function(x){
  
    read_csv()
}

macosx_study = macosx_files %>% 
  mutate(name = map(macosx_files$path, read_data)) %>% 
  unnest(cols = name) %>% 
  select(-path) %>% 
  separate(name, into = c("arm", "observation", "id")) 
  
```

```{r}
read_data = function(x){
  
  str_c("./data/", x) %>% 
    read_csv() %>% 
     pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value") %>% 
  separate(files, into = c("arm", "observation"), sep = "_") %>% 
  mutate(
    weekly_obs = str_replace(observation, "\\.csv", "")
  )
}

macosx = tibble(
  files = list.files(path = "./data/"),
  path_name = str_c("./data/", files))

tidy_macosx = macosx %>% 
  mutate(
    file_data = map(macosx %>%  
                 pull(path_name), read_data)) %>% 
  select(files, file_data) %>% 
  unnest(cols = file_data) %>% 
  janitor::clean_names() %>% 
 pivot_longer(
    week_1:week_8,
    names_to = "week",
   # names_prefix = "week_",
    values_to = "value") %>% 
  separate(files, into = c("arm", "observation"), sep = "_") %>% 
  mutate(
    weekly_obs = str_replace(observation, "\\.csv", "")
  )
```

__Problem 3__

First set the following design elements:

Fix n=30
Fix xi1 as draws from a standard Normal distribution
Fix β0=2
Fix σ2=50
Set β1=0. Generate 10000 datasets from the model
yi=β0+β1xi1+ϵi

```{r}
generate_reg = function(n = 30, beta0 = 2, beta1, var = 50) {
  
  p3_data = tibble(
  x = rnorm(n, mean = 0, sd = 1),
  y = beta0 + beta1 * x + rnorm(n, 0, var^0.5)
)
  
  ls_fit = lm(y ~ x, data = p3_data)
  
  tidy(ls_fit)
}

results = 
  rerun(10000, generate_reg(n = 30, var = 50, beta1 = 0)) %>% 
  bind_rows() %>% 
  select(term, estimate, p.value) %>% 
  filter(term == "x")


power = tibble(
  beta_1 = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output = map(.x = beta_1, ~rerun(10000, generate_reg(beta1 = .x))),
    est = map(output, bind_rows)) %>% 
  select(-output) %>% 
  unnest(est) %>% 
  select(beta_1, term, estimate, p.value) %>% 
  filter(term == "x")

final = power %>% 
  group_by(beta_1) %>% 
  summarize(sum_p = sum(p.value < 0.05),
            total_p = sum_p/n()) %>% 
  ggplot(aes(x = beta_1, y = total_p))+
  geom_bar(stat = "identity", fill = "purple")+
  labs(title = "association between effect size & power",
       x = "true value of beta1",
       y = "power") +
  theme(plot.title = element_text(hjust = 0.5))

final
```

